Inference methods comparison for the simplified Naomi model using Pareto-smoothed importance sampling

### 2023-05-09 src/naomi-simple_psis/psis.Rmd
Import objfull into PSIS notebook, and look at lp__ from tmbstan #41

```{r}
tmb <- readRDS("depends/tmb.rds")
aghq <- readRDS("depends/aghq.rds")
adam <- readRDS("depends/adam.rds")
adam_time <- adam$time
adam <- adam$adam
tmbstan <- readRDS("depends/tmbstan.rds")

@@

## Run details {.tabset}

For more information about the conditions under which these results were generated, see:

### `TMB`

```{r}
dependency_details <- function(i) {
  report_name <- names(depends[[i]])
  print(paste0("Inference results obtained from ", report_name, " with the query ", depends[[i]][[report_name]]$id))
  report_id <- orderly::orderly_search(query = depends[[i]][[report_name]]$id, report_name)
  print(paste0("Obtained report had ID ", report_id, " and was run with the following parameters:"))
  print(orderly::orderly_info(report_id, report_name)$parameters)
}

dependency_details(1)
```

### `aghq`

```{r}
dependency_details(2)
```

### `adam`

```{r}
dependency_details(3)
```

### `tmbstan`

```{r}
tmbstan_details <- dependency_details(4)
tmbstan_details
```

@@

Suppose we have two sets of samples from the posterior.
For each sample we are going to want to evaluate the log-likelihood, so that we can calculate the log-likelihood ratios.
We can extract the `TMB` objective function for the log-likelihood as follows:

```{r}
tmb$fit$obj$fn()
#' To write!
```

>>>>

```{r}
tmb <- readRDS("depends/tmb.rds")
aghq <- readRDS("depends/aghq.rds")
tmbstan <- readRDS("depends/tmbstan.rds")

@@

@@

Suppose we have two sets of samples from the posterior.
For each sample we are going to want to evaluate the log-likelihood, so that we can calculate the log-likelihood ratios.

Although we can extract a `TMB` objective function from `tmb` directly, it would correspond to the Laplace approximation.
As such we use a new objective function using `naomi_simple.cpp` directly:

```{r}
objfull <- readRDS("depends/objfull.rds")
objfull$fn(objfull$par)
```

The samples from `tmbstan` have the following values of `lp__`.
These should be equal to what would be obtained by putting the sample into `objfull$fn` (check this):

```{r}
tmbstan_samples <- rstan::extract(tmbstan$mcmc$stanfit)

data.frame(
  y = tmbstan_samples$lp__,
  x = 1:length(tmbstan_samples$lp__)
) %>%
  ggplot(aes(x = x, y = y)) +
    geom_point(alpha = 0.4) +
    labs(y = "Log-likelihood", x = "Draw number") +
    theme_minimal() 
```

Need to write a function which reformats `TMB` or `tmbstan` samples to be evaluated using `objfull$fn`:

```{r}
objfull$par

#' TODO
```
